### 2021-05-14 content/80.formal-definition.tex
Changes from Nick and others

From this formalized language `$\mathbb{L}$ro-crate` an RO-Crate can be interpreted in any representation that can gather these descriptions, their properties, classes, and literal attributes.  
\end{markdown}

>>>>

From this formalised language `$\mathbb{L}$ro-crate` an RO-Crate can be interpreted in any representation that can gather these descriptions, their properties, classes, and literal attributes.  
\end{markdown}
